### 2019-08-01 paper/paper.tex
Input sequence segment embeddings

>>>>

Another part of the input sequence given to BERT is the segment embeddings - a number from {0, 1} which signifies wether the current token is part of the first sentece or the second. After trial and error, it was found that we perform best when giving a value of 1 for \emph{each} of the answer tokens, and 0 for the question tokens. That makes sense, as part of the desire for symmetry in our model, and the fact that BERT wasn't trained with a possibilty for a third sentence, so using, for example, the number 2 for our second answer would not make any sense to it.

\subsection{Pair scores integration}
